The relative roles of genetic, ecological and environmental factors in species radiations

### 2017-11-02 paper/draft.tex
lay out shortcomings in disc

Besides adaptive radiations(/evolution), changes in or different measures of geographic isolation (landscape complexity) can give rise to non-adaptive radiations.

@@

\section{Discussion}

>>>>

Besides adaptive radiations(/evolution), changes in or different measures of geographic isolation (landscape complexity) can also give rise to non-adaptive radiations.

@@

\section{Discussion}
Shortcomings. (/Processes/Factors not considered.)
(Dynamic) resource availability: assumed constant in model, but petentially more variation, complexity in community dynamics.
Interaction: in present model only indirect interaction via competition, but predation, parasitation, herbivory, mutualism will increase complexity.
Especially pollination is assumed to be an important interaction, because having a high impact on evolution and establishment of species due to specialization.
[maybe some words on trophic interactions.]
